\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\usepackage{placeins} 
\usepackage{float}    

\title{Problem Statement and Goals\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Sep/23/2024 & Aryan Patel & Developed Problem Statement and Stretch Goals 
sections\\
Sep/23/2024 & Krish Patel & Refined sections Problem Statment, Stretch Goals as 
well as developed Challenge Level and Extras and Reflection sections\\

\bottomrule
\end{tabularx}
\end{table}

\section{Problem Statement}

\subsection{Problem}

Dairy farmers face significant challenges in managing the health, productivity,
and breeding outcomes of their herds. Traditionally, these issues are managed 
reactively, with farmers responding to problems such as health declines, 
breeding failures, or unexpected herd turnover after they occur. This reactive 
approach leads to inefficiencies, financial losses, and reduced herd 
performance. Our project, in collaboration with CATTLEytics Inc., aims to 
address these challenges by implementing a machine learning (ML) model capable 
of predicting breeding success rates and the likelihood of animals leaving the 
herd based on historical data. This model will help farmers transition from 
reactive to proactive herd management, improving overall farm productivity and 
decision-making. The model will integrate with CATTLEytics Inc.'s existing 
systems, allowing seamless adoption by farmers.

% \wss{You should check your problem statement with the
% \href{https://github.com/smiths/capTemplate/blob/main/docs/Checklists/
% ProbState-Checklist.pdf}
% {problem statement checklist}.} 

% \wss{You can change the section headings, as long as you include the required
% information.}



\subsection{Inputs and Outputs}

\paragraph{Inputs} \ \\
\\
The software will use historical herd data related to health, productivity, and 
breeding outcomes. This data may include metrics such as individual animal 
health records, breeding attempts, and farm-specific environmental conditions. 
The input data will be fed into a machine learning model to generate 
predictions.

\paragraph{Outputs} \ \\
\\
The output will consist of predictive insights aimed at improving farm 
management. These will include:
\begin{enumerate}
    \item Predictions about the success of breeding attempts for individual 
    animals.
    \item The likelihood of an animal leaving the herd.
    \item Alerts about potential health issues or productivity declines.
\end{enumerate}

The software will provide clear, actionable outputs to guide decision-making, 
presented in a format easily interpretable by farmers and other stakeholders.



\subsection{Stakeholders}

\begin{enumerate}
    \item \textbf{Farmers:} The primary users of the software, who will benefit 
    from improved herd management and decision-making.
    \item \textbf{CATTLEytics Inc.:} The company that will deploy the software 
    to its customers and provide ongoing support.
    \item \textbf{Animal Health Experts:} Professionals who may use the 
    software to provide advice to farmers based on the predictive insights 
    generated.
    \item \textbf{Regulatory Bodies:} Organizations that may use the software 
    to monitor herd health and productivity.
    \item \textbf{Dairy Production Companies:} Organizations that may use the 
    software to optimize their supply chain and production processes.
\end{enumerate}


\subsection{Environment}

\paragraph{Hardware} \ \\
\\
The software will be deployed in farm management systems typically used on 
standard personal computers or servers. These systems may also interact with 
IoT devices used for real-time data collection on farms.
\paragraph{Software} \ \\
\\
The model will be integrated into CATTLEytics Inc.'s farm management platform,
leveraging their existing infrastructure. It will seamlessly integrate into 
the farmers' existing workflow, ensuring compatibility with the tools and 
systems they are already using.

\section{Product Goals}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{|p{0.55\textwidth}|p{0.4\textwidth}|}
\hline
\textbf{Goal} & \textbf{Importance} \\ \hline
The model accurately predicts breeding success rates for individual cows. & The 
accuracy of predictions can be measured by comparing the predicted success 
rates with actual outcomes over a defined period (e.g., a breeding cycle). A 
target accuracy rate, such as 80-90\%, can be established to define success. \\ 
\hline
The model provides predictions on the likelihood of an animal leaving the 
herd. & This can be measured by tracking the model's predictions against actual 
herd turnover rates. A success threshold (e.g., 75\% accuracy or better) for 
predicting cows that will leave the herd within a specified time frame can be 
set. \\ \hline
The system integrates seamlessly into CATTLEytics Inc.'s existing platform. & 
Success can be measured by the time taken to complete the integration and the 
absence of major system disruptions post-integration (e.g., within a 1-month 
test period, there should be less than 1\% downtime or user-reported issues). 
\\ \hline
The system offers user-friendly, actionable insights for farmers. & 
User-friendliness can be measured through user feedback surveys 
post-implementation, focusing on ease of use and clarity of insights. A target 
of 80\% or more of users rating the insights as “clear” or “actionable” can be 
set as a measurable goal. \\ \hline

\end{tabularx}
\end{table}

\FloatBarrier

\section{Stretch Goals}

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{|p{0.55\textwidth}|p{0.4\textwidth}|} 
% Boxed table with column widths
\hline
\textbf{Goal} & \textbf{Importance} \\ \hline
The model processes real-time data to provide up-to-date predictions. & 
Real-time predictions allow farmers to respond quickly to changes in herd 
dynamics, preventing potential issues. \\ \hline
The system includes a feature for predicting long-term health trends of 
individual cows. & This would enable farmers to anticipate health problems and 
intervene early, leading to better animal welfare and reduced veterinary costs. 
\\ \hline
The model can be customized for different farm sizes and breeds. & 
Customization increases the model's marketability, allowing it to be adapted to 
various farm environments and specific herd characteristics. \\ \hline
The system offers encrypted data storage and transmission to ensure data 
security. & Data security is crucial for farmers and companies that handle 
sensitive herd information. This feature increases trust and protects data 
integrity. \\ \hline
\end{tabularx}
\end{table}

\FloatBarrier

\section{Challenge Level and Extras}

The challenge level for this project is general. The project requires applying
machine learning techniques to real-world problems in dairy agriculture. This
requires a solid understanding of software engineering principles and machine
learning concepts. It also demonstrates the ability to integrate multiple
domains, such as software development, data analysis, and some domain-specific
knowledge in agriculture. An additional challenge lies in developing 
user-friendly interface and/or application that allows farmers and researches
to interact with the ML model. 

Additionally, we seek to add benchmarking, specifically for various ML 
algorithms, extensive documentation, and incorporate usability testing
for our Extras. 


\newpage{}

\section*{Appendix --- Reflection}


\textbf{What went well while writing this deliverable?} \\
Our team collaborated effectively during the process. Prior to meetings, we 
engaged in discussions, that allowed for the fair allocation of work. This
resulted in a smooth workflow, where each member was prepared to contribute. 
Additionally, the quality of the work produced aligned well with the rubric, 
which boosted our confidence that the deliverable would meet course 
expectations.

One of the major successes was establishing goals after discussions with 
CATTLEytics Inc. stakeholders. These discussions not only clarified the problem 
we are solving but also led to valuable insights into metrics needed to track 
our model's success. This deliverable opened up several points for further 
exploration, including additional work we may need to consider and 
how we would evaluate the performance of our system. \\


\textbf{What pain points did you experience during this deliverable, and how
did you resolve them?} \\
One significant challenge we encountered was understanding the domain knowledge 
specific to dairy farming and herd management. Since none of us had direct 
experience in this area, it was initially difficult to determine how we could 
effectively measure the success of the machine learning system we are building. 
We addressed this issue by having in-depth discussions with the stakeholders at 
CATTLEytics Inc., who helped clarify the domain requirements and provided key 
insights on success metrics.

Another pain point was developing stretch goals. On paper, the system followed 
a fairly straightforward process, which made it challenging to come up with 
additional features that would provide significant value. We resolved this by 
brainstorming ways to extend the system's capabilities, such as real-time data 
processing and customization for different farm sizes or breeds, to align with 
the broader goals of improving herd management. \\


\textbf{How did you and your team adjust the scope of your goals to ensure
they are suitable for a Capstone project (not overly ambitious but also of
appropriate complexity for a senior design project)?} \\
Initially, we felt the project might be too straightforward for a 
Capstone-level endeavor. To address this, we refined our scope by incorporating 
stretch goals that would leverage our prior experience while ensuring we didn't 
overextend ourselves. These stretch goals allowed us to expand the project's 
technical depth without deviating from its core objectives. We also carefully 
considered the complexities of working with both ML technologies and the dairy 
agriculture sector, factoring in the unique challenges posed by each when 
defining both our immediate goals and stretch targets. This approach helped 
ensure the project maintained a suitable level of complexity while remaining 
feasible.


\end{enumerate}  

\end{document}